\documentclass[letterpaper]{article}

\usepackage{hyperref}[blue]
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Todd Schoellman}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={7in, 9.5in},
  left=0.75in,
  top=0.75in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\subsectionfont{\normalsize}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Modify lists
\usepackage{enumitem}
\setlist{itemsep=0.1pt,topsep=0pt,label={}}

\begin{document}

% Alternatively, print name centered and bold:
\centerline{\Large \bf \name}
\vspace{1pt}
\centerline{\large February 2026}

\vspace{0.25in}

\begin{minipage}{0.4\linewidth}
  Federal Reserve Bank of Minneapolis\\
  Research Department \\
  90 Hennepin Ave. \\
  Minneapolis, MN 55401
\end{minipage}
\begin{minipage}{0.5\linewidth}
  \begin{tabular}{ll}
    Email: & \href{mailto:todd.schoellman@gmail.com}{\tt todd.schoellman@gmail.com} \\
    Homepage: & \href{https://sites.google.com/view/toddschoellman/}{\tt https://sites.google.com/view/toddschoellman/} \\
  \end{tabular}
\end{minipage}


\subsection*{Education}
\begin{itemize}
  \item PhD Economics, Stanford University, 2007. 
  \item B.S. Economics, Ohio State University, 2002.
\end{itemize}


\subsection*{Employment}

\begin{itemize}
\item Senior/Principal Research Economist, Federal Reserve Bank of Minneapolis, 2018--
\item Visiting Professor, Ohio State University, Spring 2023
\item Senior Scholar, Opportunity and Inclusive Growth Institute, Federal Reserve Bank of Minneapolis, 2017--2018
\item Assistant Professor, Arizona State University, 2010--2017
\item Assistant Professor, Clemson University, 2007--2010
\end{itemize}

\subsection*{Professional Affiliations}

\begin{itemize}
\item Associate Editor, \textit{Quarterly Journal of Economics}, January 2026 -- 
\item Associate Editor, \textit{Journal of Political Economy}, September 2025 -- 
\item Treasurer, Society for Economic Dynamics, August 2022 -- 
\item Editor, \textit{Review of Economic Dynamics}, August 2022 -- 
\item Associate Editor, \textit{Review of Economic Dynamics}, February 2020 -- August 2022
\item Associate Editor, \textit{Journal of Human Capital}, March 2023 -- 
\item Editorial Board, \textit{American Economics Journal: Macroeconomics}, January 2020--
\end{itemize}

\subsection*{Research in Progress}
\begin{itemize}
\item The Global Job Ladder (with P. Martellini and J. Sockin)
\item ``Household Insurance Around the World" (with A. Bacher, K. Donovan, P. Grübener, and L. Nord).
\end{itemize}

\subsection*{Working Papers}
\begin{itemize}
\item ``Accounting for Cross-Country Income Differences Revisited" (with D. Lagakos). January 2026. 
\item ``Labor Market Anatomy of a Macroeconomic Crisis" (with K. Donovan, W. Lu, and J. Pedtke). February 2026. Revise and resubmit, \textit{Journal of Monetary Economics}
\item ``Economic Development According to Chandler" (with N. Engbom, H. Malmberg, T. Porzio, and F. Rossi). November 2025. 
\item ``Structural Transformation by Cohort" (with A. Vindas and B. Hobijn). November 2018. 
\end{itemize}

\subsection*{Published Research}
\begin{itemize}
\item ``The Missing Middle Managers: Labor Costs, Firm Structure, and Development" (with J. Hjort and H. Malmberg). Conditionally accepted, \textit{American Economic Review: Insights}
\item ``The Global Distribution of College Graduate Quality" (with P. Martellini and J. Sockin). \textit{Journal of Political Economy}, 2024, 132(2), 434--483. 
\item ``The Role of Labor Market Frictions in Structural Transformation" (with K. Donovan). \textit{Oxford Development Studies}, 2023, 51(4), 362--374.
\item ``Labor Market Dynamics and Development" (with K. Donovan and W. Lu). \textit{Quarterly Journal of Economics}, 2023, 138(4), 2287--2325. 
\item ``Skilled Labor Productivity and Cross-country Income Differences" (with L. Hendricks). \textit{American Economic Journal: Macroeconomics}, 2023, 15(1), 240--268. 
\item ``College Quality and Attendance Patterns: A Long-Run View" (with C. Herrington and L. Hendricks). \textit{American Economic Journal: Macroeconomics}, 2021, 13(1), 184--215. 
\item ``Life-Cycle Human Capital Accumulation Across Countries: Lessons from U.S. Immigrants" (with D. Lagakos, B. Moll, T. Porzio,  and N. Qian). \textit{Journal of Human Capital}, 2018, 12(2), 305--342. 
\item ``Human Capital and Development Accounting: New Evidence from Wage Gains at Migration" (with L. Hendricks). \textit{Quarterly Journal of Economics}, 2018, 133(2), 665--700. 
\item ``Life-Cycle Wage Growth Across Countries" (with D. Lagakos, B. Moll, T. Porzio, and N. Qian). \textit{Journal of Political Economy}, 2018, 126(2), 797--849. 
\item ``Wages, Human Capital, and Barriers to Structural Transformation" (with B. Herrendorf). \textit{American Economic Journal: Macroeconomics}, 2018, 10(2), 1--23.  
\item ``Early Childhood Human Capital and Development". \textit{American Economic Journal: Macroeconomics}, 2016, 8(3), 145-174. 
\item ``Why is Measured Productivity so Low in Agriculture?" (with B. Herrendorf). \textit{Review of Economic Dynamics}, 2015, 18(4), 1003--1022. 
\item ``Environmental Regulations and the Welfare Effects of Job Layoffs in the United States: A Spatial Approach" (with N. Kuminoff and C. Timmins). \textit{Review of Environmental Economics and Policy}, 2015, 9(2), 198--218. 
\item ``Student Abilities During the Expansion of U.S. Education" (with L. Hendricks). \textit{Journal of Monetary Economics}, 2014, 63(2), 19--36. 
\item  ``Families as Roommates: Changes in U.S. Household Size from 1850 to 2000" (with A. Salcedo and M. Tertilt). \textit{Quantitative Economics}, 2012,  3(1), 133--175.
\item ``Education Quality and Development Accounting", \textit{Review of Economic Studies}, 2012, 79(1), 388--417. 
\item ``The Occupations and Human Capital of U.S. Immigrants", \textit{Journal of Human Capital}, 2010, 4(1), 1--34.
\item ``Marriage Laws and Growth in Sub-Saharan Africa" (with M. Tertilt), \textit{American Economic Review Papers and Proceedings}, 2006, 96(2), 295--298.
\end{itemize}



\subsection*{Research in Progress}
\begin{itemize}
\item The Global Job Ladder (with P. Martellini and J. Sockin)
\end{itemize}

%\subsection*{Academic Visits}
%\begin{itemize}
%\item Federal Reserve Bank of St. Louis (2016, 2013, 2012, 2011)
%\end{itemize}
%\item Federal Reserve Bank of Minneapolis (2012)


\subsection*{Recent Seminars}
\begin{itemize}
\item \textbf{2026}: St. Louis Fed, planned: Carlos III, CEMFI
\item \textbf{2025}: Carnegie Mellon, Atlanta Fed, Penn State, Seoul National University
\item \textbf{2024}: Columbia, Wisconsin, Richmond Fed, Mannheim, EIEF, Hong Kong University
\item \textbf{2023}: Georgia, UC - Irvine, Johns Hopkins - SAIS, Yale, NYU, Monash, Melbourne, University of New South Wales, Ohio State
\item \textbf{2022}: Connecticut, VAMS, Duke, Edinburgh, EUI, Autonoma de Barcelona, Toronto Metropolitan
\item \textbf{2021}: Tsinghua, Central Bank of Chile,  Williams, Colby, ESADE, Carnegie Mellon
\item \textbf{2020}: Clemson, Bank of Canada, Brown, Princeton, Iowa State, York University, McGill
\item \textbf{2019}:  World Bank, UC -- San Diego
\end{itemize}
%\item \textbf{2018}:  Toronto, Atlanta Fed, Alberta, British Columbia, Connecticut, Warwick, Royal Holloway, Queen Mary, Cornell 
%\item \textbf{2017}:  Oslo, IIES, UAB, Western Ontario
%\item \textbf{2016}: Philadelphia Fed, Chicago Fed, St. Louis Fed, Pittsburgh, Notre Dame 
%\item \textbf{2015}:  ITAM, Getulio Vargas Foundation (Rio)
%\item \textbf{2014}:  Ottawa, Berkeley, Konstanz, Zurich, Mannheim, Frankfurt, UC -- San Diego, Purdue, Indiana, Notre Dame 
%\textsc{2013:}		& Western Ontario, Toronto, York, British Columbia \\
%\textsc{2012:}		& Minneapolis Fed, Ohio State, UC -- Davis \\ 
%\textsc{2011:}		& St. Louis Fed \\ 
%\textsc{2010:} 		& Arizona State, Cleveland State, South Carolina, Florida International \\
%\textsc{2009:} 		& Temple \\
%\textsc{2008:}		& North Carolina, Cleveland Fed \\
%\textsc{2007:}		& Illinois, Oxford (Nuffield), Missouri, Western Ontario, Clemson \\
%\end{longtable}

\subsection*{Recent Conference Presentations}
\begin{itemize}
\item \textbf{2026}: STEG Annual Conference, planned: UCSD Micro-to-Macro Development Workshop
\item \textbf{2025}: Philadelphia Macro Workshop, SED, IDB Macro-Development Workshop
\item \textbf{2024}: STEG Annual Conference, Exeter Workshop on Structural Transformation, Migration \& Organizations Conference, Chicago Fed Growth and Development Conference, SED, Dynare Conference Singapore (Keynote Speaker)
\item \textbf{2023}: Washington University Growth \& Development Conference, LAEF 2nd Annual Labor Market and Macroeconomic Outcomes, SED
\item \textbf{2022}: Conference on the Impact of Immigrants on Productivity, Firms, and Human Capital, Richmond Fed, SED, NBER Growth Meeting, Herrendorf Memorial Conference
\item \textbf{2021}: SED, Human Capital Conference at St. Louis Fed
\item \textbf{2019}: SED, Cowles Conference on Macroeconomics, Vienna Macro Cafe, Temple Macro-Growth Workshop 
\end{itemize}
% \item \textbf{2018}: SED, Macroeconomics and Business CYCLE, Canadian Macro Study Group
%\item \textbf{2017}: Conference on Human Capital and Financial Frictions, Georgetown University; Thinking Big Conference on Macroeconomics; SED; Edinburgh Workshop on Agricultural Productivity, Rural-Urban Migration, and Structural Transformation; Philadelphia Search and Matching
%\item \textbf{2016}: NBER Growth Meeting; CIREQ Conference on Human Capital and Inequality; SED 
%\item \textbf{2015}: Midwest Macro; SED; Becker-Friedman Conference in Honor of the Life and Work of Gary Becker; NBER Time \& Space; HKUST Conference on Urbanization, Structural Change, and Employment 
%\item \textbf{2014}: SED; RIDGE Workshop on Productivity Growth, Resource Misallocation and Development 
%\textsc{2013:}		&  NBER Growth Meeting; Society for Economic Dynamics; Tsinghua Workshop in Macroeconomics; Growth and Development Conference (St. Louis); Vienna Macroeconomics Cafe; ASU Conference on the Development of Human Capital \\
%\textsc{2012:}		& SED; Midwest Macro; Growth and Development Conference (Toronto); NBER Growth Meeting \\ 
%\textsc{2011:}		& Midwest Macro; SED \\
%\textsc{2010:} 		& SED; NBER/BREAD Conference on Economic Development; LACEA TIGN Conference; Southern Growth Conference \\
%\textsc{2009:} 		& Econometric Society (Summer \& Winter); NBER Time \& Space; Midwest Macro; SED \\
%\textsc{2008:}		& Midwest Macro \\
%\textsc{2007:}		& Midwest Macro; SED; Conference on Economic Development \\
%\end{longtable}

\subsection*{Recent Discussions}
\begin{itemize}
\item ``Unequal Global Convergence" by Chatterjee, Giannone, Kleineberg, Kuno, and Looser (NBER EFEG, Summer 2025)
\item ``The Long-Term Distributional and Welfare Consequences of Covid-19 School Closures" by Fuchs-Sch\"{u}ndeln, Krueger, Ludwig, and Popova (CHCS Employment Conference, Fall 2020)
\item ``Accounting for Cross-Country Income Differences: New Evidence from Multinational Firms" by Alviarez, Cravino, and Ramondo (NBER EFEG, Summer 2020)
\item ``Labor Market Search, Informality and Schooling Investments" by Bobba, Flabbi, and Levy (Y-Rise 2019)
\item ``Migration Costs and Observational Returns to Rural-Urban Migration" by Lagakos, Marshall, Mobarak, Waugh, and Vernot (Carnegie-Rochester 2019)
\item ``Selection and Absolute Advantage in Farming and Entrepreneurship: Microeconomic Evidence and Macroeconomic Implications" by Alvarez-Cuadrado, Amodio, and Poschke (CMSG 2019)
\item ``Occupational Choice and the Dynamics of Human Capital, Inequality and Growth" by Dvorkin and Monge-Naranjo (System Committee Meeting on Macroeconomics, Spring 2019)
\item ``Skilled Immigration, Firms, and Policy" by Mehra at NBER IFM, Winter 2019. 
%\item ``Structural Change in Investment and Consumption: A Unified Approach" by Herrendorf, Rogerson, and Valentinyi at NBER Economic Growth Small Group, Winter 2018
%\item ``The Rise of Meritocracy and the Inheritance of Advantages" by Comerford, Rodriguez Mora, and Watts at Vienna Macro Cafe 2016
%\item ``Explaining Cross-Cohort Differences in Life-Cycle Earnings" by Kong, Ravikumar, and Vandenbroucke at Vienna Macro Cafe, 2015
%\item ``The Agricultural Productivity Gap in Developing Countries" by Gollin, Lagakos, and Waugh at AEA, 2013
%\item ``Human Capital Portfolios" by Silos and Smith at Canadian Macro Study Group, 2012
%\item  ``Equilibrium Effects of Education Policies: A Quantitative Evaluation" by Gallipoli, Meghir, and Violante at CIREQ, 2011
\end{itemize}

\subsection*{Advising}

\subsubsection*{Main Advisor}
\begin{itemize}
\item Alex Rivadeneira (2019, Banco de Mexico) 
\item	Alberto Rivera-Padilla (2019, Cal State -- Fullerton)
\item	Minjuan Sun (2018, Future-Moves Group)
\item	Rishabh Sinha (2015, World Bank Research Division) 
\end{itemize}
						
\subsubsection*{Committee}
\begin{itemize}
\item Bipul Verma (planned 2026)
\item Jacob Wright (2026, Queensland)
\item Katerina Gribbin (2025, Reserve Bank of Australia)
\item Joey Pedtke (2024, Clemson)
\item Sean Bassler (2024, Amazon)
\item Joao Fonseca Rodrigues (2022, Amazon)
\item Vladimir Smirnyagin (2020, Yale SOM Postdoc) 
\item David Bradley (2019, Analysis Group) 
\item Ryan Wessel (2017, LDS Institute of Religion) 
\item Adam Blandin (2016, Virginia Commonwealth University) 
\item Xican Xi (2016, Fudan University) 
\item Andy Ge (2015, Chinese Security Regulatory Committee) 
\item Jaehan Cho (2014, Korea Institute for Industrial Economics and Trade) 
\item Kevin Donovan (2013, Notre Dame)
\item Chris Herrington (2013, University of South Alabama)
\item Paul Schreck (2011, analyst position at Minneapolis Fed) 
\end{itemize}

\subsection*{Teaching Experience}
\begin{itemize}
\item PhD: Growth and Development Topics Course 
\item MBA: Macro/International
\item Undergraduate: Principles of Macro, Intermediate Macro, Growth \& Development, International, Trade
\end{itemize}


%\subsection{Service}\vspace{-5mm}
%\begin{longtable}[l]{rp{14.1cm}}
%\textsc{Department:} & Hiring Committee (2014--15) \\
%	& Macroeconomics Seminar Coordinator (2013--15) \\ 
%	& Undergraduate Curriculum Committee (2010--12) \\ 
%\\
%\textsc{Conferences:} & Program Committee, Society for Economic Dynamics Meeting, 2012--2015 \\ 
%& Co-organizer, Young Scholars Conference: Growth \& Development (ASU), 2016 \\ 
%& Co-organizer, Public Policy from School to Retirement (ASU), 2013 \\ 
%& Co-organizer, Quantitative Macroeconomics Conference (ASU), 2012 \\ 
%& Co-organizer, Macroeconomics Reunion Conference (ASU), 2012 \\
%& Co-organizer, Conference on Human Capital (ASU), 2011 \\ 
%\multicolumn{2}{c}{} \\
%\textsc{Refereeing:} & Numerous journals, including American Economic Review; Quarterly Journal of Economics; Econometrica; Review of Economic Studies; Journal of the European Economic Association; International Economic Review; American Economic Journal: Macroeconomics; Journal of Economic Growth; Review of Economic Dynamics; Journal of Development Economics. \\
%\end{longtable}


\end{document}